---
title: "Curriculum Vitae"
author: ''
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    highlight: textmate
    theme: flatly
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
subtitle: ''
---


```{r Pacotes, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)                                
library(car)                                
library(rstatix)                                
library(emmeans)
library(ggplot2)
library(knitr)
library(kableExtra)
library(htmltools)
```


<style>h1 {font-size: 28px;}
       h1.title {font-size: 32px;}
       h2 {font-size: 22px;}
       h3 {font-size: 16px;}
       h4 {font-size: 12px;}
       h5 {font-size: 10px;}
       h6 {font-size: 08px;}
       code {color: inherit; background-color: rgba(0, 0, 0, 0.04);}
       pre:not([class]) { background-color: white }
</style>


  
# Eduardo Vaz de Lima  
Lean IT | PMP | ACP | CSM | Project Management


## Contact
Tel: 19 98330 4636  
e-mail: lima.vaz.eduardo@gmail.com  
LinkedIn: [linkedin.com/in/eduardo1lima](https://www.linkedin.com/in/eduardo1lima/ "Eduardo Lima's LinkedIn")  
Campinas   
São Paulo, Brazil    
  
  
# About
```
I've been learning about software development projects every since I finished college.  
I have seen many technologies coming and going. 
Many programming languages glowing and fading away.  
Many management approaches fighting to be number one.  

What I have learned so far?  
I’ve learned that people create successful projects, not tools.  
Successful projects are defined by the customer.  
People should be the priority and also, Continuous Improvement is the only way to go.  
```


  
# Qualifications:
- Professional experienced in Software Development Projects, with many hours logged in projects using both, traditional approach as well as Agile methodologies.

- **Jira** Cloud administrator and **Kanban** heavy user.

- Believer that:
  - *People* should be the *priority*, 
  - *Continuous improvement* is the way to go,
  - *Communication* plays a major role in achieving the objectives.

- Experienced **instructor** in training employees to use department tools and procedures.

- Continuous learner, got certified in PMI-PMP®, PMI-ACP®, CSM and Lean IT Foundation.

- With strong *international experience*, has worked/studied abroad in Sweden, England and the USA.

- Familiar with working in multicultural overseas groups. 
  

  

# Experience

## DHL Supply Chain
Senior Integration Specialist  
Feb 2018 – Present

- Our team makes it possible to connect a customer's logistic request to a DHL
warehouse system and vice versa. Since companies' EDIs do not share a common standard,
we create software maps to make sure the correct translation takes place.

- Responsible for introducing a new way of managing software projects for NORAM and
LATAM regions using Jira tool, translating business requirements into
stories, improving communication with developers using tasks and sub-tasks.

- Introduced the concept of management by *Key Performance Indicators*, using data 
extracted from Jira and the concept of collecting *Customer Satisfaction* data.

- Passionate for automation of daily routine tasks, created a script to summarize
necessary information, in a standard way, to be sent to overseas development team.

- Facilitator of a team of developers spread in Asia and Americas, managing scope, 
time and budget.
  


## Instituto de Pesquisas Eldorado  
Senior Software Engineer  
May 2015 – Mar 2017  

- Worked on a end to end project aimed to transfer Android certification process 
(Radio-Frequency, Safety and Radiation Absorption) from Motorola US to Lenovo 
headquarters in Asia, saving a great amount of man-hours due to the implementation 
of an comprehensive documenting processes, reducing communication noise among teams located at 
China, US and Brazil.


## Ericsson Telecommunication GSDC
System Integration Engineer  
Sept 2005 – Dec 2013

- Worked as a point of contact for a particular product, RPC, in the Global 
Software Distribution Center, GSDC.

- Our team, Modification Handling, achieved international recognition by avoiding 
data configuration errors with a simple xml/xsd file structure which helped the 
Software Supply Information System to save hundreds of man-hours in three countries, 
Canada, Mexico and Brazil.

- Worked in configuration/integration projects on telecommunication 
equipment at important telecom operators in Brazil and USA.

- With the help of friends, I was able to design some simple tools that helped 
minimize common errors in configuration files, speeding up the processes and 
greatly appreciated by the night shift engineers.

- My last position was in Pre-Software Sales department, as a member of a Scrum 
development team, providing accurate data of operator's network, to be included 
in a technical report, used by key account managers in order to increase new sales 
opportunities. Sales went up considerably during the project.

  
# Education  
## Formal

```{r, echo = FALSE, message = FALSE, warning = FALSE}
ed <- tribble(
  ~escola,~curso, ~ano,
  "Faculdade de Engenharia Industrial - FEI", "Engineer's Degree, Electrical and Electronics Engineering", "1986 - 1991",
  "Universidade Estadual de Campinas - UNICAMP", "Engineer's Degree, Clinical Engineering", "1994 - 1995",
  "Fundação Getulio Vargas - FGV", "Business Administration and Management, General", "1998 - 2000",
  "Universidade Estadual de Campinas - UNICAMP", "Engineer's Degree, Object Oriented Programming", "2003 - 2004"
)
# glimpse(ed)

kable(head(ed, 10), col.names = c("Institution", "Subject", "Year")) %>%
  kable_styling(full_width = F, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```
  
## Courses

```{r, echo = FALSE, message = FALSE, warning = FALSE}
courses <- tribble(
  ~name, ~school, ~year,
  "Jira Administration - Server - 8.5", "Atlassian University", "2020",
  "Data Science: R Basics", "HarvardX", "2020",
  "AFIGP - Academia de Formação de Instrutores de Projetos PMISP", "PMI SP", "2017",
  "Agile Lego Challenge", "PMI-SP", "2017",
  "Finance Mathematics and Excel", "Universidade Estadual de Campinas", "2011"
  
)

kable(head(courses, 10), col.names = c("Institution", "Subject", "Year")) %>%
  kable_styling(full_width = F, bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```




  
# Certifications

## Lean IT Foundation (LITA)
- Issue date: July 2020
- Certification Number: 6342243.20795754
- [See credential](https://app.exeed.pro/holder/badge/64689)

## PMI Agile Certified Practitioner (PMI-ACP)®  
- Issue date: March 2018
- Certification Number: 2167691
- [See credential](https://www.youracclaim.com/badges/da494590-2ef9-467c-b19e-f0b2ef588c21/linked_in_profile)

## Project Management Professional (PMP)®
- Issue date: February 2015
- Certification Number: 1789797
- [See credential](https://www.youracclaim.com/badges/040bafc3-b813-439b-9334-a65cb5178b41)

## Ericsson Certified Technology-IP (ECT-IP)
- Issue date: August 2013


# Volunteer
## ATEAC - Atividades, Terapias e Educação Assistida por Animais de Campinas
[ATEAC](http://ateac.org.br/) 
2011 - now.  
Children assisted therapy with dogs.  
We take dogs to the Pediatric ward, and walk with the kids, in exchange for a smile :)
  

