---
title: "Eduardo Lima"
author: "19 98330 4636"
date: ""
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Contact
19 98330 4636 (Mobile)

[lima.vaz.eduardo@gmail.com](mailto:lima.vaz.eduardo@gmail.com)<br>
[LinkedIn](https://www.linkedin.com/in/eduardo1lima/ "Eduardo Lima's LinkedIn")

## Objective
Project Manager


## About
> I have been learning about Software Development Projects every since I finished college.<br>
I have seen many technologies coming and going.<br>
Many programming languages glowing and fading away.<br>
Many management approaches fighting to be number one.<br>

> What I have learned so far … ?<br>
I’ve learned People create successful projects, not tools.<br>
Successful projects are defined by the customer.<br>
People should be the priority as well as Continuous Improvement is the only way to go.<br>

## Qualifications:
Professional experienced in Software Development Projects, with many hours logged in projects using both, traditional approach as well as Agile methodologies.

Jira Cloud administrator and Kanban heavy user.

Believer that people should be the priority, continuous improvement is the way to go and communication plays a major role in achieving the objectives.

Experienced Instructor training employees to use department tools and procedures.

Continuous learner, got certified in PMI-PMP®, PMI-ACP®, CSM and Lean IT Foundation.

With strong international experience, has worked/studied abroad in Sweden, England and the USA.

Familiar with working in multicultural overseas groups. 

## Experience
### DHL Supply Chain
Senior Integration Specialist<br/>
Feb 2018 – Present

- Our team makes it possible to connect a customer's logistic request to a DHL
warehouse and vice versa. Since companies' EDIs do not share a common standard,
we create software maps to make sure the correct translation takes place.

- Responsible for introducing a new way of managing software projects for NORAM and
LATAM regions, using Jira environment, translating business requirements into
stories, improving communication with developers using tasks and sub-tasks and
extracting important project data to stakeholders through a set of Key Performance
Indicators, fetched from Jira.

- Kanban heavy user. Currently Jira Cloud administrator.

- Experienced Instructor in training employees to use department tools and
procedures.

- Passionate for automation of daily routine tasks, created a script to summarize
necessary information, in a standard way, to be sent to overseas development team.
Believer that communications plays an important role in project success.

- Facilitator of a team of developers spread in Asia and Americas.
---
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
